Density dependence

### 2020-09-15 R/density dependence.Rmd
added flowering probability

```{r}
m_surv <- glmer(surv ~ log_shts_prev + density_0_10 + density_10_20 + (1|plot) + (1|ha_id_number) + (1|year), 
                family = binomial, data = ha_cf)
```

@@

```{r}
m_surv2 <- glmer(surv ~ log_shts_prev + density_0_10 + density_10_20 + (1|plot) + (1|year), 
                family = binomial, data = ha_cf)
AICtab(m_surv, m_surv2)
```
Can remove plant ID
```{r}
m_surv3 <- glmer(surv ~ log_shts_prev + density_0_10 + density_10_20 + (1|year), 
                family = binomial, data = ha_cf)
AICtab(m_surv2, m_surv3)
```
Can't remove plot

```{r}
m_surv4 <- glmer(surv ~ log_shts_prev + density_0_10 + density_10_20 + (1|plot), 
                family = binomial, data = ha_cf)
AICtab(m_surv2, m_surv4)
```
Can't remove year.

@@

```{r}
Anova(m_surv2)
```

Yes, but only immediate grid cell

@@

- try negative binomial distribution for shoot number
- ~~Density should be total shoot number~~
- ~~Should actually be density in previous year~~
- ~~Shoots should be poisson distribution, not log-transformed?~~
- incorporate 1-ha fragments and use habitat type as a predictor.
- Implement FLM approach to density dependence.

>>>>

Should this be a function of `log_shts` or `log_shts_prev`?  Think about how you've coded survival.

```{r}
m_surv <- glmer(surv ~ log_shts + density_0_10 + density_10_20 + (1|plot) + (1|ha_id_number) + (1|year), 
                family = binomial, data = ha_cf)
```

@@

```{r}
m_surv2 <- glmer(surv ~ log_shts + density_0_10 + density_10_20 + (1|plot) + (1|year), 
                family = binomial, data = ha_cf)
AICtab(m_surv, m_surv2)
```
Can remove plant ID
```{r}
m_surv3 <- glmer(surv ~ log_shts + density_0_10 + density_10_20 + (1|year), 
                family = binomial, data = ha_cf)
AICtab(m_surv2, m_surv3)
```
Can't remove plot

```{r}
m_surv4 <- glmer(surv ~ log_shts + density_0_10 + density_10_20 + (1|plot), 
                family = binomial, data = ha_cf)
AICtab(m_surv2, m_surv4)
```
Can't remove year.

@@

```{r}
Anova(m_surv2)
fixef(m_surv2) %>% plogis()
```

Marginal, and only immediate grid cell.  Density has positive affect on survival.  So, probably just good patches.

# Flowering probability

```{r}
ggplot(ha_cf, aes(infl)) + geom_histogram()
```
Make a binary column

```{r}
ha_cf <- 
  ha_cf %>% 
  mutate(flwr = as.integer(infl>0), .before = infl)

#the way suvival is currently coded, a plant can flower and then not survive in the same year, so no need to filter out dead plants.
ha_cf %>% filter(surv == 0)
```

```{r}
m_flwr <- glmer(flwr ~ log_shts_prev + density_0_10 + density_10_20 + (1|ha_id_number) + (1|plot) + (1|year), family = binomial, data = ha_cf)
```

```{r}
m_flwr2 <- glmer(flwr ~ log_shts_prev + density_0_10 + density_10_20 + (1|ha_id_number) + (1|year), family = binomial, data = ha_cf)
AICtab(m_flwr, m_flwr2)
```
can get rid of plot ID

```{r}
m_flwr3 <- glmer(flwr ~ log_shts_prev + density_0_10 + density_10_20 + (1|year), family = binomial, data = ha_cf)
AICtab(m_flwr, m_flwr2, m_flwr3)
```
keep plant ID

```{r}
m_flwr4 <- glmer(flwr ~ log_shts_prev + density_0_10 + density_10_20 + (1|ha_id_number), family = binomial, data = ha_cf)
AICtab(m_flwr, m_flwr2, m_flwr3, m_flwr4)
```

keep year

```{r}
Anova(m_flwr2)
fixef(m_flwr2) %>% plogis()
```

Ok, there's an effect, but oddly only past 20m.  Again, positive density dependence.

@@

- Check number of inflorescencesa given flowered?
- check that survival is coded right so that it is a function of `ht_prev`
- try negative binomial distribution for shoot number
- ~~Density should be total shoot number~~
- ~~Should actually be density in previous year~~
- ~~Shoots should be poisson distribution, not log-transformed?~~
- incorporate 1-ha fragments and use habitat type as a predictor.
- Implement FLM approach to density dependence.
